\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-02-07 analysis/paper/casebase-manuscript.Rmd
update last table
Other minor changes

---
author:
  - name: Sahir Rai Bhatnagar*
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon*
    affiliation: 'University of Manitoba'
    address: >
      186 Dysart Road
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: https://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James A. Hanley
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title: "\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
abstract: |
  | In epidemiological studies of time-to-event data, a quantity of interest to the clinician and the patient is the risk of an event given a covariate profile. However, methods relying on time matching or risk-set sampling (including Cox regression) eliminate the baseline hazard from the likelihood expression or the estimating function. The baseline hazard then needs to be estimated separately using a non-parametric approach. This leads to step-wise estimates of the cumulative incidence that are difficult to interpret. Using case-base sampling, Hanley & Miettinen (2009) explained how the parametric hazard functions can be estimated using logistic regression. Their approach naturally leads to estimates of the cumulative incidence that are smooth-in-time.
  | In this paper, we present the **casebase** R package, a comprehensive and flexible toolkit for parametric survival analysis. We then describe how the case-base framework can be used in more complex settings: non-linear functions of time and non-proportional hazards, competing risks, and variable selection. Our package also includes an extensive array of visualization tools to complement the analysis of time-to-event data. We illustrate all these features through three different case studies.
  | *SRB and MT contributed equally to this work.
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{graphicx}
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{makecell}
  \usepackage{tabu}
  \DeclareUnicodeCharacter{2500}{-}
  \newcommand{\proglang}{\textsf}
output: rticles::rjournal_article 
bibliography: casebase-manuscript.bib 
fig_width: 12
fig_height: 9
fig_caption: true
editor_options: 
  chunk_output_type: console
---

@@

In the following sections, we illustrate the main functions of the \pkg{casebase} package through three case studies; each one showcasing a different analysis type. First, we show how to model different functional forms of time as well as non-proportional hazards. Then we perform a competing risks analysis and compare our results with the Fine-Gray model. The third case study illustrates how to perform variable selection in dataset with a large number of covariates.

@@

For our first case study, we return to the ERSPC study and investigate the differences in risk between the control and screening arms. We fit four models that differ in which functional form of time is used: 1) excluded from the linear predictor as seen in \eqref{eq:exp}, 2) linear function as seen in \eqref{eq:gomp}, 3) log function as seen in \eqref{eq:weibull}, and 4) a smooth function using cubic B-splines. The models are fit using \code{fitSmoothHazard} with the familiar formula interface:

```{r, eval = eval_cs1, echo = -1}
set.seed(12)
fmla <- list(exponential = as.formula(DeadOfPrCa ~ ScrArm),
             gompertz = as.formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
             weibull = as.formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
             splines = as.formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))

fits <- lapply(fmla, function(i) {
  fitSmoothHazard(i, data = ERSPC, ratio = 100)
})
```

The output object from \code{fitSmoothHazard} inherits from the \code{singleEventCB} and \code{glm} classes. As such, we can directly use the \code{summary} generic:

```{r, eval = FALSE, echo=TRUE}
summary(fits[["splines"]]) 
```

```{r, eval = eval_cs1, echo=FALSE}
print.summary.glm <- function(x,digits=max(3,getOption("digits")-3),symbolic.cor=x$symbolic.cor,
                              signif.stars = getOption("show.signif.stars"),show.call=FALSE,show.resids=FALSE,...) {
  if (show.call) cat("Call:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"), "\n", sep = "")
  if (show.resids) {
    cat("Deviance Residuals: \n")
    if (x$df.residual > 5) {
      x$deviance.resid <- stats::quantile(x$deviance.resid, na.rm = TRUE)
      names(x$deviance.resid) <- c("Min", "1Q", "Median", "3Q", "Max")
    }
    xx <- zapsmall(x$deviance.resid, digits + 1)
    print.default(xx, digits = digits, na.print = "", print.gap = 2)
    cat("\n")
  }
  if (length(x$aliased) == 0L) cat("No Coefficients\n")
  else {
    df <- if ("df" %in% names(x)) x[["df"]]
    else NULL
    if (!is.null(df) && (nsingular <- df[3L] - df[1L])) 
      cat("Coefficients: (", nsingular, " not defined because of singularities)\n", sep = "")
    else cat("\nCoefficients:\n")
    coefs <- x$coefficients
    if (!is.null(aliased <- x$aliased) && any(aliased)) {
      cn <- names(aliased)
      coefs <- matrix(NA, length(aliased), 4L, dimnames = list(cn,colnames(coefs)))
      coefs[!aliased, ] <- x$coefficients
    }
    stats::printCoefmat(coefs, digits = digits, signif.stars = signif.stars,na.print = "NA", ...)
  }
  cat("\n(Dispersion parameter for ", x$family$family, " family taken to be ", 
      format(x$dispersion), ")\n\n", apply(cbind(paste(format(c("Null","Residual"), 
                                                              justify = "right"), "deviance:"),
                                                 format(unlist(x[c("null.deviance","deviance")]), digits = max(5, digits + 1)), " on", 
                                                 format(unlist(x[c("df.null", "df.residual")])), " degrees of freedom\n"),1L,
                                           paste, collapse = " "), sep = "")
  if (nzchar(mess <- stats::naprint(x$na.action))) cat("  (", mess, ")\n",sep="")
  cat("AIC: ",format(x$aic,digits=max(4,digits+1)),"\n\n",
      "Number of Fisher Scoring iterations: ",x$iter,"\n",sep="")
  correl <- x$correlation
  if (!is.null(correl)) {
    p <- NCOL(correl)
    if (p > 1) {
      cat("\nCorrelation of Coefficients:\n")
      if (is.logical(symbolic.cor) && symbolic.cor) print(stats::symnum(correl,abbr.colnames=NULL))
      else {
        correl <- format(round(correl, 2),nsmall=2,digits=digits)
        correl[!lower.tri(correl)] <- ""
        print(correl[-1,-p,drop=FALSE],quote=FALSE)
      }
    }
  }
  cat("\n")
  invisible(x)
}

@@

Next, the \code{absoluteRisk} function takes as input the \code{fitSmoothHazard} object and returns a matrix where each column corresponds to the covariate profiles specified in the \code{newdata} argument, and each row corresponds to a specified time point:

```{r, eval=FALSE, echo=echo_plot_code}
new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
new_time <- seq(0,14,0.1)

risks <- lapply(fits, function(i) {
  absoluteRisk(object = i, time = new_time, newdata = new_data, method = "mont")
})
```

In Figure \ref{fig:erspc-cox-cif}, we overlay the estimated CIFs from \pkg{casebase} on the Cox model CIF. The CIF estimates for the exponential model in panel (1) overestimate the cumulative incidence earlier on in time, and underestimate it later on. Based on our earlier discussion of the population-time plot, this poor fit for the exponential hazard was expected. We notice a better fit with increasing complexity of our model for time in Figure \ref{fig:erspc-cox-cif} (panels 2--4). As noted above, the usual asymptotic results hold for likelihood ratio tests built using case-base sampling models. Therefore, we can easily test the null hypothesis that the exponential model is just as good as the larger (in terms of number of parameters) spline model:

@@

Previous re-analyses of these data suggested that the overall screening attributed reduction in death due to prostate cancer of 20% was an underestimate [@hanley2010mortality]. The estimated 20% (from a proportional hazards model) did not account for the delay between screening and the time the effect is expected to be observed. As a result, the null effects in years 1–7 masked the substantial reductions that began to appear from year 8 onwards. This motivates the use of a time-dependent hazard ratio which can easily be fit with the \pkg{casebase} package by including an interaction term with time in the model:

@@

With this first case study, we explored how \pkg{casebase} allows us to fit different parametric survival models with possible time-varying effects, and how we can compare the fit of each model with tools from GLMs.

@@

```{r bmtcrr-casebase-weibull, warning = FALSE, eval = eval_cs2}
model_cb <- fitSmoothHazard(
  Status ~ ftime + Sex + D + Phase + Source + Age,
  data = bmtcrr,
  ratio = 100,
  time = "ftime"
)
```

@@

In this third case study, we showed how case-base sampling can be used in conjunction with penalized logistic regression to perform variable selection in survival models.

@@

In this article, we presented the \proglang{R} package \pkg{casebase}, which provides functions for fitting smooth parametric hazards and estimating CIFs using case-base sampling. Our package also provide several functions to produce graphical summaries of the data and the results. We outlined the theoretical underpinnings of the approach, we provided details about our implementation, and we illustrated the merits of the approach and the package through three case studies.

As a methodological framework, case-base sampling is very flexible. Some of this flexibility has been explored before in the literature: for example, Saarela and Hanley [-@saarela2015case] used case-base sampling to model a time-dependent exposure variable in a vaccine safety study. As another example, Saarela and Arjas [-@saarela2015non] combined case-base sampling and a Bayesian non-parametric framework to compute individualized risk assessments for chronic diseases. In the case studies above, we further explored this flexibility along two fronts. On the one hand, we showed how splines could be used as part of the linear predictor to model the effect of time on the hazard. This strategy yielded estimates of the survival function that were qualitatively similar to semiparametric estimates derived from Cox regression; however, case-base sampling led to estimates of the survival function that *vary smoothly in time* and are thus easier to interpret. On the other hand, we also displayed the flexibility of case-base sampling by showing how it could be combined with penalized logistic regression to perform variable selection. Furthermore, the second case study showed how case-base sampling can be applied to competing risks settings. It should be noted that the three case studies presented above only considered covariates that were fixed at baseline. In the package vignette, we use the Stanford Heart Transplant data [@clark1971cardiac,@crowley1977covariance] to show how case-base sampling can also be used in the context of time-dependent exposure. In this study, the exposure period was defined as the week following vaccination. Hence, the main covariate of interest, i.e. exposure to the vaccine, was changing over time. In this context, case-base sampling offers an efficient alternative to nested case-control designs or self-matching.

@@

\begin{table}
\caption{\label{tab:compCBvsCox}Comparison between the Cox model and case-base sampling}
\centering
\begin{tabular}[t]{llp{5cm}}
\toprule
Feature & Cox model & Case-base sampling\\
\midrule
Model type & Semi-parametric & Fully parametric\\
Time & Left hand side of the formula & Right hand side (allows flexible modeling of time)\\
Cumulative incidence & Step function & Smooth-in-time curve\\
Non-proportional hazards & Interaction of covariates with time & Interaction of covariates with time\\
Model testing &  & Use GLM framework \newline (e.g.\ LRT, AIC, BIC)\\
\addlinespace
Competing risks & Difficult & Cause-specific CIFs\\
% Prediction & Kaplan-Meier-based & ROC, AUC, risk reclassification probabilities\\
\bottomrule
\end{tabular}
\end{table}

>>>>

---
author:
  - name: Sahir Rai Bhatnagar*
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon*
    affiliation: 'University of Manitoba'
    address: >
      186 Dysart Road
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: https://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James A. Hanley
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title: "\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates"
abstract: |
  | In epidemiological studies of time-to-event data, a quantity of interest to the clinician and the patient is the risk of an event given their covariate profile. However, methods relying on time matching or risk-set sampling (including Cox regression) eliminate the baseline hazard from the likelihood expression or the estimating function. The baseline hazard then needs to be estimated separately using a non-parametric approach. This leads to step-wise estimates of the cumulative incidence that are difficult to interpret. Using case-base sampling, Hanley & Miettinen (2009) explained how the parametric hazard functions can be estimated using logistic regression. Their approach naturally leads to estimates of the cumulative incidence that are smooth-in-time.
  | In this paper, we present the **casebase** R package, a comprehensive and flexible toolkit for parametric survival analysis. We describe how the case-base framework can be used in more complex settings: non-linear functions of time and non-proportional hazards, competing risks, and variable selection. Our package also includes an extensive array of visualization tools to complement the analysis of time-to-event data. We illustrate all these features through three different case studies.
  | * SRB and MT contributed equally to this work.
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{longtable}
  \usepackage{graphicx}
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{makecell}
  \usepackage{tabu}
  \DeclareUnicodeCharacter{2500}{-}
  \newcommand{\proglang}{\textsf}
output: rticles::rjournal_article 
bibliography: casebase-manuscript.bib 
fig_width: 12
fig_height: 9
fig_caption: true
editor_options: 
  chunk_output_type: console
---

@@

In this section, we illustrate the main functions of the \pkg{casebase} package through three case studies. Each one showcases a different type of analysis. First, we show how to model different functional forms of time as well as non-proportional hazards. Then we perform a competing-risk analysis and compare our results with the Fine-Gray model. The third case study illustrates how to perform variable selection in high-dimensional datasets.

@@

For our first case study, we return to the ERSPC study and investigate the differences in risk between the control and screening arms. We fit four models that differ in which functional form of time is used: 1) excluded from the linear predictor (Eq. \eqref{eq:exp}); 2) linear function (Eq. \eqref{eq:gomp}); 3) log function (Eq. \eqref{eq:weibull}); and 4) a smooth function using cubic B-splines. The models are fit using \code{fitSmoothHazard} with the familiar formula interface:

```{r, eval = eval_cs1, echo = -1}
set.seed(12)
fmla <- list(exponential = formula(DeadOfPrCa ~ ScrArm),
             gompertz = formula(DeadOfPrCa ~ Follow.Up.Time + ScrArm),
             weibull = formula(DeadOfPrCa ~ log(Follow.Up.Time) + ScrArm),
             splines = formula(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm))

fits <- lapply(fmla, function(form) {
  fitSmoothHazard(form, data = ERSPC, ratio = 100)
})
```

The output object from \code{fitSmoothHazard} inherits from the \code{singleEventCB} and \code{glm} classes. For this reason, we leveraged the \code{summary} method for \code{glm} objects to output a familiar summary of the results:

```{r, eval = TRUE, echo=eval_cs1}
summary(fits[["splines"]]) 
```

```{r, eval = FALSE, echo=FALSE}
print.summary.glm <- function(x,digits=max(3,getOption("digits")-3),symbolic.cor=x$symbolic.cor,
                              signif.stars = getOption("show.signif.stars"),show.call=FALSE,show.resids=FALSE,...) {
  if (show.call) cat("Call:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"), "\n", sep = "")
  if (show.resids) {
    cat("Deviance Residuals: \n")
    if (x$df.residual > 5) {
      x$deviance.resid <- stats::quantile(x$deviance.resid, na.rm = TRUE)
      names(x$deviance.resid) <- c("Min", "1Q", "Median", "3Q", "Max")
    }
    xx <- zapsmall(x$deviance.resid, digits + 1)
    print.default(xx, digits = digits, na.print = "", print.gap = 2)
    cat("\n")
  }
  if (length(x$aliased) == 0L) cat("No Coefficients\n")
  else {
    df <- if ("df" %in% names(x)) x[["df"]]
    else NULL
    if (!is.null(df) && (nsingular <- df[3L] - df[1L])) 
      cat("Coefficients: (", nsingular, " not defined because of singularities)\n", sep = "")
    else cat("\nCoefficients:\n")
    coefs <- x$coefficients
    if (!is.null(aliased <- x$aliased) && any(aliased)) {
      cn <- names(aliased)
      coefs <- matrix(NA, length(aliased), 4L, dimnames = list(cn,colnames(coefs)))
      coefs[!aliased, ] <- x$coefficients
    }
    stats::printCoefmat(coefs, digits = digits, signif.stars = signif.stars,na.print = "NA", ...)
  }
  cat("\n(Dispersion parameter for ", x$family$family, " family taken to be ", 
      format(x$dispersion), ")\n\n", apply(cbind(paste(format(c("Null","Residual"), 
                                                              justify = "right"), "deviance:"),
                                                 format(unlist(x[c("null.deviance","deviance")]), digits = max(5, digits + 1)), " on", 
                                                 format(unlist(x[c("df.null", "df.residual")])), " degrees of freedom\n"),1L,
                                           paste, collapse = " "), sep = "")
  if (nzchar(mess <- stats::naprint(x$na.action))) cat("  (", mess, ")\n",sep="")
  cat("AIC: ",format(x$aic,digits=max(4,digits+1)),"\n\n",
      "Number of Fisher Scoring iterations: ",x$iter,"\n",sep="")
  correl <- x$correlation
  if (!is.null(correl)) {
    p <- NCOL(correl)
    if (p > 1) {
      cat("\nCorrelation of Coefficients:\n")
      if (is.logical(symbolic.cor) && symbolic.cor) print(stats::symnum(correl,abbr.colnames=NULL))
      else {
        correl <- format(round(correl, 2),nsmall=2,digits=digits)
        correl[!lower.tri(correl)] <- ""
        print(correl[-1,-p,drop=FALSE],quote=FALSE)
      }
    }
  }
  cat("\n")
  invisible(x)
}

@@

Next, the \code{absoluteRisk} function takes as input the \code{singleEventCB} object and returns a matrix where each column corresponds to the covariate profiles specified in the \code{newdata} argument, and each row corresponds to time points specified by the \code{time} argument:

```{r, eval=FALSE, echo=echo_plot_code}
new_data <- data.frame(ScrArm = c("Control group", "Screening group"))
new_time <- seq(0, 14, by = 0.1)

risks <- lapply(fits, function(fit) {
  absoluteRisk(fit, time = new_time, newdata = new_data)
})
```

In Figure \ref{fig:erspc-cox-cif}, we overlay the estimated CIFs from \pkg{casebase} on the Cox model CIF. The CIF estimates for the exponential model in panel (1) overestimate the cumulative incidence earlier on in time, and underestimate it later on. Based on our earlier discussion of the population-time plot, this poor fit for the exponential hazard was expected. We notice a better fit with increasing complexity of our model for time in Figure \ref{fig:erspc-cox-cif} (panels 2--4). As noted in Theoretical Details section, the usual asymptotic results hold for likelihood ratio tests built using case-base sampling models. Therefore, we can easily test the null hypothesis that the exponential model is just as good as the larger (in terms of number of parameters) spline model:

@@

Previous re-analyses of these data suggested that the overall screening attributed reduction in death due to prostate cancer of 20% was an underestimate [@hanley2010mortality]. The estimated 20% (from a proportional hazards model) did not account for the delay between screening and the time the effect is expected to be observed. As a result, the null effects in years 1–7 masked the substantial reductions that began to appear from year 8 onward. This motivates the use of a time-dependent hazard ratio which can easily be fit with the \pkg{casebase} package by including an interaction term with time in the model:

@@

<!-- With this first case study, we explored how \pkg{casebase} allows us to fit different parametric survival models with possible time-varying effects, and how we can compare the fit of each model with tools from GLMs. -->

@@

```{r bmtcrr-casebase-weibull, warning = FALSE, eval = eval_cs2, echo = TRUE}
model_cb <- fitSmoothHazard(
  Status ~ ftime + Sex + D + Phase + Source + Age,
  data = bmtcrr,
  ratio = 100,
  time = "ftime"
)
```

@@

<!-- In this third case study, we showed how case-base sampling can be used in conjunction with penalized logistic regression to perform variable selection in survival models. -->

@@

In this article, we presented the \proglang{R} package \pkg{casebase}, which provides functions for fitting smooth parametric hazards and estimating CIFs using case-base sampling. Our package also provides several functions to produce graphical summaries of the data and the results. We outlined the theoretical underpinnings of the approach, we provided details about our implementation, and we illustrated the merits of the approach and the package through three case studies.

As a methodological framework, case-base sampling is very flexible. Some of this flexibility has been explored before in the literature: for example, Saarela and Hanley [-@saarela2015case] used case-base sampling to model a time-dependent exposure variable in a vaccine safety study. As another example, Saarela and Arjas [-@saarela2015non] combined case-base sampling and a Bayesian non-parametric framework to compute individualized risk assessments for chronic diseases. In the case studies above, we further explored this flexibility along two fronts. On the one hand, we showed how splines could be used as part of the linear predictor to model the effect of time on the hazard. This strategy yielded estimates of the survival function that were qualitatively similar to semiparametric estimates derived from Cox regression; however, case-base sampling led to estimates of the survival function that *vary smoothly in time* and are thus easier to interpret. On the other hand, we also displayed the flexibility of case-base sampling by showing how it could be combined with penalized logistic regression to perform variable selection. Furthermore, the second case study showed how case-base sampling can be applied to competing risks settings. It should be noted that the three case studies presented above only considered covariates that were fixed at baseline. In one of the package vignettes, we use the Stanford Heart Transplant data [@clark1971cardiac,@crowley1977covariance] to show how case-base sampling can also be used in the context of time-dependent exposure. In this study, the exposure period was defined as the week following vaccination. Hence, the main covariate of interest, i.e. exposure to the vaccine, was changing over time. In this context, case-base sampling offers an efficient alternative to nested case-control designs or self-matching.

@@

\begin{table}
\caption{\label{tab:compCBvsCox}Comparison between the Cox model and case-base sampling}
\centering
\begin{tabular}[t]{llp{5cm}}
\toprule
Feature & Cox model & Case-base sampling\\
\toprule
Model type & Semi-parametric & Fully parametric\\\midrule
Time & Left hand side of the formula & Right hand side (allows flexible modeling of time)\\\midrule
Cumulative incidence & Step function & Smooth-in-time curve\\\midrule
Non-proportional hazards & Interaction of covariates with time & Interaction of covariates with time\\\midrule
Model testing & Likelihood-ratio tests, score tests, & Use GLM framework\\
 & information criteria & (e.g.\ LRT, AIC, BIC)\\\midrule
\addlinespace
Competing risks & Difficult & Cause-specific CIFs\\
% Prediction & Kaplan-Meier-based & ROC, AUC, risk reclassification probabilities\\
\bottomrule
\end{tabular}
\end{table}
